Query Optimization for Dynamic Imputation

### 2017-03-01 paper/algorithm.tex

We extend these heuristics to 
account for the new operators: \textit{Drop} and \textit{Impute}. \textit{Drop} is a special case of a sequential scan, and its time
complexity can be expressed as a function of the number of heap pages read and the I/O cost
per page. The time computation for \textit{Impute} depends on the properties of the underlying
algorithm. \ProjectName{} treats the actual machine learning algorithm as a black box
and simply queries it for a time estimate. In our reference implementation,
we use an iterative algorithm (see~\Cref{sec:imputation}), where the runtime cost
is a function of the number of attributes with no missing data, number of attributes with
missing data being imputed, number of tuples, and the number of iterations for the algorithm.

>>>>

We extend these heuristics to 
account for the new operators: \textit{Drop} and \textit{Impute}. \textit{Drop} is a special case of a sequential scan, and its time
complexity can be expressed as a function of the number of heap pages read and the I/O cost
per page. The time computation for \textit{Impute} depends on the properties of the underlying
algorithm. \ProjectName{} treats the actual machine learning algorithm as a black box
and simply queries it for a time estimate. In the implementation of our system,
we use an iterative algorithm (see~\Cref{sec:imputation}), where the runtime cost
is a function of the number of attributes with no missing data, number of attributes with
missing data being imputed, number of tuples, and the number of iterations for the algorithm.
